---
title: "GSS challange"
author: "Alejandra Magdaleno"
date: "October 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
GSS <-read.csv(file="GSScsv.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is belief in the bigbang theory (BIGBANG) independent of belief in an afterlife (POSTLIFE)?

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~POSTLIFE + BIGBANG,data=GSS)
barchartGC(~POSTLIFE + BIGBANG,data=GSS, type="percent")

```
  
The graphs tells us that there are more people that believe in the after life than those who do not.  Of the people who believe in the afterlife a larger number and percentage of them believe that the big bang theory is false. Of the people who do not believe in the afterlife, a larger number believe that the big bank theory is true. This information leads us to believe there might be a statistical differece, but further numerical and inferential results need to be observed. 
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~POSTLIFE + BIGBANG, data=GSS)
rowPerc(table1)
colPerc(table1)
```
From the people that do not believe in the post life, 34.78% say the Big Bang theory is false and 65.22% believe it is true.  From the people that do believe in the post life, 56.77% believe the big bang theory is false and 43.23% believe that it is true.  These numerical results seem to support the graphical results observed.      
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
Let's consider the odds for a bit.  Of those who stated that they did not believe in the post life, the odds of them saying that the big bang is false is 8/15(.5333).  Of those that stated that they believed in the after life, the odds that they said they believed in the big bang theory is 88/67(1.31).  The odds are .408:1.  With the probability of occurence being P=.0801, we will not be able to reject the null hypothesis.  The null hypothesis be accepted. 
```{r}
(8/15)/(88/67)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
